Open Source, Collaborative Curriculum

### 2017-04-28 siip.tex
budget table

          Attempts at this have been made before. Most notable among 
          these is Software Carpentry (which with the PI is quite involved). 
          Unfortunately, our experience showed that 
          forks of the original material tend to diverge without any strong 
          incentive for contribution back to the master material 
          \cite{wilson_software_2014,wilson_software_2014-1}. We expect that fine-grained modularity 
          of lesson components and a clear dependency graph of prerequisite 
          modules for each lesson may assist in overcoming the challenges 
          encountered by Software Carpentry and others.

@@

          \section{Budget Justification}
          The two workshops will 
          Explain travel for external collaborators, meals, meeting space, etc. 
          Host it in the Union?

>>>>

          Attempts at this have been made before. Most notable among 
          these is Software Carpentry (with which the PI and Co-PI are quite involved). 
          Software Carpentry teaches computational skills for scientists using 
          a shared curriculum hosted on GitHub. Unfortunately, our experience showed that 
          forks of the original material tend to diverge without any strong 
          incentive for contribution back to the master material 
          \cite{wilson_software_2014,wilson_software_2014-1}. We expect that fine-grained modularity 
          of lesson components and a clear dependency graph of prerequisite 
          modules for each lesson may assist in overcoming the challenges 
          encountered by Software Carpentry and others.

@@

          \section{Budget}
          The two workshops will be hosted at the Illini Union, where a meeting 
          room will be reserved. Visiting 
          invited workshop participants will be flown to Urbana-Champaign and 
          lodged at the Illini Union Hotel.

\begin{tabular}[htb]{|l|c|c|c|}
        \hline
        \textbf{Item} & \textbf{Cost} & \textbf{Units} & \textbf{Notes} \\ 
        \hline
        \textbf{Lodging} & <++> & <++> & <++> \\ 
        \textbf{<++>} & <++> & <++> & <++> \\ 
        \textbf{<++>} & <++> & <++> & <++> \\ 
        \textbf{<++>} & <++> & <++> & <++> \\ 
        \textbf{<++>} & <++> & <++> & <++> \\ 
        \textbf{<++>} & <++> & <++> & <++> \\ 
        \textbf{<++>} & <++> & <++> & <++> \\ 
        \textbf{<++>} & <++> & <++> & <++> \\ 
        \textbf{<++>} & <++> & <++> & <++> \\ 
        \hline
\end{tabular}
